Malacology: A Programmable Storage System Built on Ceph

### 2016-05-08 paper/paper.tex
modified:   paper.tex 	Fixed cite and bibliography commands

\usepackage{times}
\usepackage{multirow}
\usepackage{arydshln}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{biblatex}
\bibliography{refs}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Malacology: A Programmable Storage System Built on Ceph},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{5}

@@

To illustrate the benefits and challenges of this approach we examine
the programmability of Ceph \autocite{weil_ceph_2006}, the increasingly
popular, production-level open-source distributed storage system.
Something of a storage swiss army knife, Ceph supports file, block, and
object interfaces simultaneously in a single cluster. Ceph's Reliable Autonomous Distributed Object Storage (RADOS) system is a cluster of storage
devices (OSDs) that provide Ceph with data durability and integrity
using replication, erasure-coding, and scrubbing
\autocite{weil_rados_2007}. 
% By introducing
% programmability concepts into Ceph, we can build new services by
% carefully exposing internal storage services to applications.

@@

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    A high-performance distributed shared log service called Zlog which is based on CORFU~\autocite{balakrishnan_corfu_2012}
  \item
    A re-implementation of the programmable Mantle metadata load balancing service using Malacology~\autocite{sevilla:sc15-mantle}
  \item 
    An application of the Mantle metadata load balancing service to manage 
  \end{enumerate}
\end{itemize}

@@

So called ``bolt-on'' services are third-party solutions integrated into a
system to provide functionality and improve performance for common use-cases
(e.g. a metadata service). The introduction of additional services may provide
simplicity and performance enhancements, but ``bolt-on`` services often
duplicate functionality, unnecessarily increasing the likelihood of bugs or
introducing unpredictable performance problems. For example, we are developing
a high-performance distributed shared-log on Ceph called ZLog, based on the
CORFU protocol~\cite{corfu}. Serialization at high-performance is achieved using a
``sequencer'' service that maintains a volatile, in-memory counter used to assign a log
position to each client that appends to the log. One option for building
a distributed log is to use PAXOS, or an out-of-the-box solution such as
Zookeeper. However, these systems adhere to the pre-coneived notions of
storage, namely that data is safe from data loss, which is exactly the feature
that causes traditional approaches to run at significantly reduced speed.

@@

For example, SciHadoop \autocites[
]{buck:hpc2011-scihadoop}{buck:sc2013-scidr} changes both the Hadoop
application and the Hadoop framework itself to leverage the structure of
scientific data (3D array-based data, more specifically) to increase
performance, locality, and the number of early results. This is not a
bad proposition, but creates a coupling that is highly tied to the
underlying physical properties of the system, making it difficult to
adapt to future changes at the storage system level.

@@

Tuning large and complicated systems is difficult because of the number
of parameters (e.g., Hadoop 2.7.1 has 210 tunables) and because the
tunables are difficult to understand or quantify (e.g., Ceph tunables
\autocite{sevilla:sc15-mantle}). To succesfully tune the system, a
developer must have domain and system specific knowledge. Without this
intimate knowledge, the tuning turns into somewhat of a black art, where
the only way to figure out the best settings is trial and error.

Auto-tuning techniques attempt to find a good solution among a huge space of
available system configurations. However, in practice auto-tuning is limited
to only the configuration tunables that the storage system exposes and can be
overwhelmed with too many parameters.  For instance, auto-tuning may be
capable of identifying instances in which new data layouts would benefit a
workload, but unless the system can provide such a transformation, the option
is left off the table.  Starfish \autocite{herodotou:cidr2011-starfish} made
an attempt of this for Hadoop but this technique would need to severely limit
the space of parameters in order to feasible, similar to the approach used in
\autocite{behzad:sc2013-autotuning}.

@@

As a last resort, the application developer can alter the storage system
itself. In the best case a developer is using an open-source system in which
case one must become familiar with often enormous code-bases before being able
to make changes, but then face the task of approaching a community to
integrate changes, or be forced to maintain an in-house version and risk
maintaining features that become incompatible.  A successful example of this
is the work that focused on HDFS scalability for metadata-intensive workloads
\autocite{shvachko_hdfs_2010}. This has lead to modifications to its
architecture or API \autocite{balmin:sigmod2012-clydesdale} to improve
performance.

@@

\being{comment}
As an example use-case, ZLog needs to
store metadata information with each object so for each operation, it
checks the epoch value and write capability (2 metadata reads) and
writes the index (metadata write).
\end{comment}

@@

\begin{comment}
\begin{figure}[htbp]
\centering
\includegraphics{figures/obj-int-dev-churn.png}
\caption{Source code changes over time indicate the dynamic interface
development will need to support a high frequency of interface churn.
Each dot represents a Ceph commit with a corresponding number of lines
of code changed. \label{fig:obj-int-dev-churn}}
\end{figure}
\end{comment}

@@

Ceph provides storage by striping and replicating data across RADOS
~\cite{weil_rados_2007}, the reliable distributed object store. RADOS
uses many techniques to ensure that data is not corrupted or lost, such
as erasure coding, replication, and data scrubbing. Furthermore, many of
these techniques try to be autonomous so that work is distributed across
the cluster. For example, when placement groups change the OSDs
rebalance and re-shard data in the background in a process called
placement group splitting.

@@

Malacology adds new hooks to Ceph and a new interface class for both the
MDS and OSD that uses Lua
\autocite{ierusalimschy:lua15}\autocite{ierusalimschy:spe96}. Our
framework has added a mechanism for defining and running object and
metadata balancer classes using Lua. Our Lua bindings expose functions
and symbols both ways; the host program can call functions defined in
Lua and the Lua scripts can call functions defined in native C++. These
bindings are merged upstream. We choose Lua for 4 reasons: performance,
portabability, size, and and security.

Lua is a fast scripting language. It was designed to be an embedded
language and the LuaJIT virtual machines boasts near-native performance
\autocite{pall:luajit15}\autocite{grawinkel_pdsw12}. Lua is frequently
used in game engines to set policies but we use it here because most of
the user-defined object classes in Ceph are policies as well (see
\S\ref{table:objclasses}). Separating policy from mechanism is a driving
factor in using Lua.

@@

This effectively decouples policy from mechanism, which helps future
designers explore trade-offs and isolates policy development from
code-hardened systems. Decoupling policy mechanism is not a new
technique but designing the storage system with programmability as a
first-class citizen is credits policy/mechanism separation as the
biggest reason for the success of the block allocation mechanisms in the
Fast File System\textasciitilde{}\autocite{mckusick:fast2015-FFS} yet there
are no mechanisms for transparently exposing and modifying the
underlying logic in modern file systems.

@@

Lua is a performs well as an embeddable scripting language. Although it
is an interpreted language, the bindings are designed to make the
exchange of variables and functions amongst languages straightforward.
The LuaJIT virtual machine boasts near-native performance, making it a
logical choice for scriptability frameworks in systems research
\autocite{neto:dls14-luaos}. In storage systems, it has been effectively
used both on \autocites[
]{grawinkel:pdsw2012-lua}{watkins2013:bdmc13-in-vivo} and off
\autocite{sevilla:sc15-mantle} the critical path, where performance is
important. Lua is frequently used in game engines to set policies but we
use it here because most of the user-defined classes in Ceph are
policies as well! We do not want to provide specific implementations,
like pulling data from objects or transferring them over the network,
but instead strive to say \emph{what to do} with the data once we have
it. Separating policy from mechanism is a driving factor in using Lua.

@@

The other two advantages, that Lua leaves a small memory footprint and
that is is secure, are discussed at length in \autocites[
]{ierusalimschy_programming_2006}{neto:dls14-luaos}. In short, Lua
provides relatively robust sandbox capabilities for protecting the
system against some malicious cases, but does not protect the system
from poor policies. Since Malacology does not use these features (yet),
we will avoid discussion here.

@@

Many distributed file systems decouple metadata and data I/O so that
these services can scale independently \autocites[
]{alam:pdsw2011-metadata-scaling}[ ]{ghemawat:sosp2003-gfs}[
]{hildebrand:msst2005-pnfs}[ ]{weil_ceph_2006}[
]{welch:fast2008-panasas}{shvachko:login2012-hdfs-scalability}. Despite
this optimization, scaling the metadata services is still difficult
because metadata accesses impose small and frequent requests on the
underlying storage syste \autocite{roselli:atec2000-FS-workloads}. Many
techniques for designing the metadata services have been proposed to
accommodate this workload: Lustre
\autocite{konstantinos:pdsw2014-lustre-metadata}, GFS
\autocite{ghemawat:sosp2003-gfs}, and HDFS
\autocite{shvachko:login2012-hdfs-scalability} keep all metadata on one
server; GIGA+ \autocite{patil:fast2011-giga}, IndexFS
\autocite{ren:sc2014-indexfs}, Lazy Hybrid
\autocite{brandt:msst2003-lh}, GPFS \autocite{schmuck:fast2002-gpfs},
and pNFS \autocite{hildebrand:supercomputing2006-pNFS} hash the file
system namespace across a dedicated cluster and cache metadata; Panasas
\autocite{welch:fast2008-panasas} and CephFS
\autocite{weil:sc2004-dyn-metadata} partition the file system namespace
into \# d assign them to servers. These systems have novel mechanisms
for Mantle \autocite{sevilla:sc15-mantle} is a programmable metadata
balancer that separates the metadata balancing policies from their
mechanisms. Admistrators inject code to change how the metadata cluster
distributes metadata. In the paper, we showed how to implement a single
node metadata service, a distributed metadata services with hashing, and
a distributed metadata service with dynamic subtree partitioning.

@@

Malacology uses the same Active and Typed Storage module presented in
DataMods \autocite{watkins_datamods_2012}; Asynchronous Service and File
Manifolds can be implemented with small changes to the Malacology
framework, namely asynchronous object calls and Lua stubs in the inode,
respectively.

@@

\printbibliography

>>>>

\usepackage{times}
\usepackage{multirow}
\usepackage{arydshln}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
%\usepackage{biblatex}
%\bibliography{paper}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Malacology: A Programmable Storage System Built on Ceph},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{5}

@@

To illustrate the benefits and challenges of this approach we examine
the programmability of Ceph~\cite{weil_ceph_2006}, the increasingly
popular, production-level open-source distributed storage system.
Something of a storage swiss army knife, Ceph supports file, block, and
object interfaces simultaneously in a single cluster. Ceph's Reliable Autonomous Distributed Object Storage (RADOS) system is a cluster of storage
devices (OSDs) that provide Ceph with data durability and integrity
using replication, erasure-coding, and scrubbing~\cite{weil_rados_2007}. 
% By introducing
% programmability concepts into Ceph, we can build new services by
% carefully exposing internal storage services to applications.

@@

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi}.}
  \itemsep1pt\parskip0pt\parsep0pt
  \item
    A high-performance distributed shared log service called Zlog which is based on CORFU~\cite{balakrishnan_corfu_2012}
  \item
    A re-implementation of the programmable Mantle metadata load balancing service using Malacology~\cite{sevilla:sc15-mantle}
  \item 
    An application of the Mantle metadata load balancing service to manage 
  \end{enumerate}
\end{itemize}

@@

So called ``bolt-on'' services are third-party solutions integrated into a
system to provide functionality and improve performance for common use-cases
(e.g. a metadata service). The introduction of additional services may provide
simplicity and performance enhancements, but ``bolt-on'' services often
duplicate functionality, unnecessarily increasing the likelihood of bugs or
introducing unpredictable performance problems. For example, we are developing
a high-performance distributed shared-log on Ceph called ZLog, based on the
CORFU protocol~\cite{corfu}. Serialization at high-performance is achieved using a
``sequencer'' service that maintains a volatile, in-memory counter used to assign a log
position to each client that appends to the log. One option for building
a distributed log is to use PAXOS, or an out-of-the-box solution such as
Zookeeper. However, these systems adhere to the pre-coneived notions of
storage, namely that data is safe from data loss, which is exactly the feature
that causes traditional approaches to run at significantly reduced speed.

@@

For example, SciHadoop~\cite{buck:hpc2011-scihadoop,buck:sc2013-scidr} changes both the Hadoop
application and the Hadoop framework itself to leverage the structure of
scientific data (3D array-based data, more specifically) to increase
performance, locality, and the number of early results. This is not a
bad proposition, but creates a coupling that is highly tied to the
underlying physical properties of the system, making it difficult to
adapt to future changes at the storage system level.

@@

Tuning large and complicated systems is difficult because of the number
of parameters (e.g., Hadoop 2.7.1 has 210 tunables) and because the
tunables are difficult to understand or quantify (e.g., Ceph tunables~\cite{sevilla:sc15-mantle}). To succesfully tune the system, a
developer must have domain and system specific knowledge. Without this
intimate knowledge, the tuning turns into somewhat of a black art, where
the only way to figure out the best settings is trial and error.

Auto-tuning techniques attempt to find a good solution among a huge space of
available system configurations. However, in practice auto-tuning is limited
to only the configuration tunables that the storage system exposes and can be
overwhelmed with too many parameters.  For instance, auto-tuning may be
capable of identifying instances in which new data layouts would benefit a
workload, but unless the system can provide such a transformation, the option
is left off the table.  Starfish~\cite{herodotou:cidr2011-starfish} made
an attempt of this for Hadoop but this technique would need to severely limit
the space of parameters in order to feasible, similar to the approach used in~\cite{behzad:sc2013-autotuning}.

@@

As a last resort, the application developer can alter the storage system
itself. In the best case a developer is using an open-source system in which
case one must become familiar with often enormous code-bases before being able
to make changes, but then face the task of approaching a community to
integrate changes, or be forced to maintain an in-house version and risk
maintaining features that become incompatible.  A successful example of this
is the work that focused on HDFS scalability for metadata-intensive workloads~\cite{shvachko_hdfs_2010}. This has lead to modifications to its
architecture or API~\cite{balmin:sigmod2012-clydesdale} to improve
performance.

@@

\if{false}
As an example use-case, ZLog needs to
store metadata information with each object so for each operation, it
checks the epoch value and write capability (2 metadata reads) and
writes the index (metadata write).
\fi

@@

\if{false}
\begin{figure}[htbp]
\centering
\includegraphics{figures/obj-int-dev-churn.png}
\caption{Source code changes over time indicate the dynamic interface
development will need to support a high frequency of interface churn.
Each dot represents a Ceph commit with a corresponding number of lines
of code changed. \label{fig:obj-int-dev-churn}}
\end{figure}
\fi

@@

Ceph provides storage by striping and replicating data across RADOS~\cite{weil_rados_2007}, the reliable distributed object store. RADOS
uses many techniques to ensure that data is not corrupted or lost, such
as erasure coding, replication, and data scrubbing. Furthermore, many of
these techniques try to be autonomous so that work is distributed across
the cluster. For example, when placement groups change the OSDs
rebalance and re-shard data in the background in a process called
placement group splitting.

@@

Malacology adds new hooks to Ceph and a new interface class for both the
MDS and OSD that uses Lua~\cite{ierusalimschy:lua15,ierusalimschy:spe96}. Our
framework has added a mechanism for defining and running object and
metadata balancer classes using Lua. Our Lua bindings expose functions
and symbols both ways; the host program can call functions defined in
Lua and the Lua scripts can call functions defined in native C++. These
bindings are merged upstream. We choose Lua for 4 reasons: performance,
portabability, size, and and security.

Lua is a fast scripting language. It was designed to be an embedded
language and the LuaJIT virtual machines boasts near-native performance~\cite{pall:luajit15,grawinkel_pdsw12}. Lua is frequently
used in game engines to set policies but we use it here because most of
the user-defined object classes in Ceph are policies as well (see
\S\ref{table:objclasses}). Separating policy from mechanism is a driving
factor in using Lua.

@@

This effectively decouples policy from mechanism, which helps future
designers explore trade-offs and isolates policy development from
code-hardened systems. Decoupling policy mechanism is not a new
technique but designing the storage system with programmability as a
first-class citizen is credits policy/mechanism separation as the
biggest reason for the success of the block allocation mechanisms in the
Fast File System~\cite{mckusick:fast2015-FFS} yet there
are no mechanisms for transparently exposing and modifying the
underlying logic in modern file systems.

@@

Lua is a performs well as an embeddable scripting language. Although it
is an interpreted language, the bindings are designed to make the
exchange of variables and functions amongst languages straightforward.
The LuaJIT virtual machine boasts near-native performance, making it a
logical choice for scriptability frameworks in systems research~\cite{neto:dls14-luaos}. In storage systems, it has been effectively
used both on \cite{grawinkel:pdsw2012-lua,watkins2013:bdmc13-in-vivo} and off
\cite{sevilla:sc15-mantle} the critical path, where performance is
important. Lua is frequently used in game engines to set policies but we
use it here because most of the user-defined classes in Ceph are
policies as well! We do not want to provide specific implementations,
like pulling data from objects or transferring them over the network,
but instead strive to say \emph{what to do} with the data once we have
it. Separating policy from mechanism is a driving factor in using Lua.

@@

The other two advantages, that Lua leaves a small memory footprint and
that is is secure, are discussed at length in~\cite{ierusalimschy_programming_2006,neto:dls14-luaos}. In short, Lua
provides relatively robust sandbox capabilities for protecting the
system against some malicious cases, but does not protect the system
from poor policies. Since Malacology does not use these features (yet),
we will avoid discussion here.

@@

Many distributed file systems decouple metadata and data I/O so that
these services can scale independently~\cite{alam:pdsw2011-metadata-scaling,ghemawat:sosp2003-gfs,hildebrand:msst2005-pnfs,weil_ceph_2006,welch:fast2008-panasas,shvachko:login2012-hdfs-scalability}. Despite
this optimization, scaling the metadata services is still difficult
because metadata accesses impose small and frequent requests on the
underlying storage syste~\cite{roselli:atec2000-FS-workloads}. Many
techniques for designing the metadata services have been proposed to
accommodate this workload: Lustre~\cite{konstantinos:pdsw2014-lustre-metadata}, GFS~\cite{ghemawat:sosp2003-gfs}, and HDFS~\cite{shvachko:login2012-hdfs-scalability} keep all metadata on one
server; GIGA+~\cite{patil:fast2011-giga}, IndexFS~\cite{ren:sc2014-indexfs}, Lazy Hybrid~\cite{brandt:msst2003-lh}, GPFS~\cite{schmuck:fast2002-gpfs},
and pNFS~\cite{hildebrand:supercomputing2006-pNFS} hash the file
system namespace across a dedicated cluster and cache metadata; Panasas~\cite{welch:fast2008-panasas} and CephFS~\cite{weil:sc2004-dyn-metadata} partition the file system namespace
into \# d assign them to servers. These systems have novel mechanisms
for Mantle~\cite{sevilla:sc15-mantle} is a programmable metadata
balancer that separates the metadata balancing policies from their
mechanisms. Admistrators inject code to change how the metadata cluster
distributes metadata. In the paper, we showed how to implement a single
node metadata service, a distributed metadata services with hashing, and
a distributed metadata service with dynamic subtree partitioning.

@@

Malacology uses the same Active and Typed Storage module presented in
DataMods~\cite{watkins_datamods_2012}; Asynchronous Service and File
Manifolds can be implemented with small changes to the Malacology
framework, namely asynchronous object calls and Lua stubs in the inode,
respectively.

@@

\bibliography{paper}
\bibliographystyle{plain}
%\printbibliography
